\chapter{Integration II}

Earlier we established integration of functions and treated the ``$dx$'' nearly as punctuation.
Another more flexible and approach is to use \emph{differential forms}.




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% DIFFERENTIAL FORMS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Differential Forms}

\begin{definition}
	A \textbf{(differential) 0-form} $\beta$ on $\mathbb{R}^n$ is a function $\beta : \mathbb{R}^n \to \mathbb{R}$.
	A \textbf{(differental) 1-form} $\omega$ on $\mathbb{R}^n$ is an expression of the form:
	\begin{equation}
		\omega = f_1(\text{x}) \; dx_1 + f_2(\text{x}) \; dx_2 + \ldots + f_n(\text{x}) \; dx_n
	\end{equation}
\end{definition}

There is very little to say about 0-forms, they are just functions on $\mathbb{R}^n$.
1-forms look very much like something we're used to integrating with.
Of course if all but one of $f_i$ are zero then we have a \emph{basic 1-form}, $\omega = f_i \; dx_i$ which is nothing new to integrate over.
Using the linearity of integration, general 1-forms can easily be seperated into a sum of integrals on basic 1-forms.
Typically, 1-forms are encountered inexplicitly in a multivariate calcululus class with Green's theorem:
\begin{equation}
	\tag{Green's Theorem}
	\int_D \left( \frac{\partial f_2}{\partial x} - \frac{\partial f_1}{\partial y}  \right) \;dx\;dy 
	=\int_{\partial D} f_1(x,y) \; dx + f_2(x,y) \; dy
\end{equation}

\todo[inline]{
Formally, $T_x(\mathbb{R}^n) \to \mathbb{R}$.


}


We can add differential forms but rather than multiplication we use the $\wedge$ product.

To create higher order $p$-forms we use the wedge operator $\wedge$. 

First of all, the wedge product is primarily defined by being \emph{anti-commutative} or \emph{skew-symmetric}.
That is, $dx \wedge dy = -dy \wedge dx$.
Several results immediately follow from this.
When used on two identical $dx$, we have $dx \wedge dx = - dx \wedge dx$ and so the result must be zero.
Additionally, for any permutation $\sigma$ of $[p]$:
\begin{equation}
	dx_1 \wedge ... \wedge dx_p = \text{sgn}(\sigma) \; dx_{\sigma(1)} \wedge ... \wedge dx_{\sigma(p)}
\end{equation}


\begin{definition}
	Given a $k$-rectangle $\Omega \in \mathbb{R}^n$ with coordinates $\text{x} = (x_1, x_2, \ldots, x_n)$
	A \textbf{differential $p$-form} $\beta$ over $\Omega$ has the form:
	\begin{equation}
		\beta = \sum_{j_1 \in [n]} \ldots \sum_{j_p \in [n]} b_{(j_1, \ldots, j_p)}(\text{x}) \; 
				\text{d} x_{j_1} \wedge \ldots \wedge \text{d} x_{j_p}
	\end{equation}
	Typically, we will take $j = (j_1, \ldots, j_p)$ and express $\beta$ as, 
	$\sum_j b_j(x) \; dx_{j_1} \wedge \ldots \wedge dx_{j_p}$.
	We denote the space of all $p$-forms on $\Omega$ by $\Lambda^p(\Omega)$.
\end{definition}


$dx^i$ and $dx^j$ are trivial differential 1-forms by taking $f_i=1$ and $f_j=1$ respectively.
When we take the wedge product of these, we end up with the 2-form $dx^i \wedge dx^j$.
It should then seem natural to think of $\wedge$ as an operator which maps 
a $k$-form and an $\ell$-form to a $(k+\ell)$-form.
For general $p$ and $q$-forms we define the wedge product.

\begin{definition}
	Let $\alpha = \sum_i a_i(x) \; dx_{i_1} \wedge \ldots \wedge dx_{i_p} \in \Lambda^p(\Omega)$ and 
	$\beta = \sum_j b_j(x) \; dx_{j_1} \wedge \ldots \wedge dx_{j_q} \in \Lambda^q(\Omega)$. We extend the
	wedge product $\wedge : \Lambda^p(\Omega) \times \Lambda^q(\Omega) \to \Lambda^{p+q}(\Omega)$ by:
	\begin{equation}
		\alpha \wedge \beta  = \sum_{i,j} a_i(x) b_j(x) \; 
			dx_{i_1} \wedge \ldots \wedge dx_{i_p} \wedge 
			dx_{j_1} \wedge \ldots \wedge dx_{j_q}
	\end{equation}
\end{definition}

Although we take all possible $\binom{n}{q} \cdot \binom{n}{p}$ pairs of 
$a_i (x) dx_{i_1} \wedge \ldots \wedge dx_{i_p}$ and $b_i (x) dx_{i_1} \wedge \ldots \wedge dx_{i_p}$,
most of the possible terms will end up being zero.
If \emph{any} of the terms in $dx_{i}$ appears in $dx_{j}$, then the wedge product will be zero 
and no term will be contributed.
As such, if $q+p > n$, there will be a duplicate in every term and so the entire sum will be zero.
When all is said and done, at most we will have $\binom{n}{p+q}$ terms.
Rather than the skew-symmetry we had when commuting $dx \wedge dy$, in higher dimensions the sign depends on 
$p \cdot q$ of the $p$-form and $q$-form we are commuting.
Specifically, 
\begin{equation}
	\alpha \wedge \beta = (-1)^{pq} \beta \wedge \alpha
\end{equation}
This can be easily seen by commuting each of $dx_{j_1}, \ldots dx_{j_q}$ terms each past 
$dx_{i_1}\wedge \ldots \wedge dx_{i_p}$. 
So we are commuting $q$ terms each past $p$ terms, reversing the sign each time for a net $(-1)^{pq}$.


The wedge product is only one part of our algebra of differential forms.
We have several other nice identities for its behaviour with addition and multiplication.
For the following, we consider $f$ to be a function on $\mathbb{R}^n$.
Additionally we consider the differential forms $\omega_1$ and $\omega_2$ to be $k$-forms, $\alpha$ to be a $p$-form
 and $\beta$ to be an $q$-form.
Then we have the following:
\begin{align}
	(\omega_1 + \omega_2) \wedge \alpha  & \;=\; \omega_1 \wedge \alpha + \omega_2 \wedge \alpha \\
	(\omega_1 \wedge \alpha) \wedge \beta & \;=\; \omega_1 \wedge ( \alpha \wedge \beta ) \\
	(f \cdot \omega_1) \wedge \alpha & \;=\;  f \cdot (\omega_1 \wedge \alpha) \;=\; \omega_1 \wedge (f \cdot \alpha)
\end{align}
These should all be quite obvious from definitions. 
We should also note the identities which are \emph{not} present.
We have defined the sum of $\omega_1$ and $\omega_2$: two differential forms which are the same dimension but not
the sum of $\alpha$ and $\beta$: differential forms with different dimension.
It is clear how one would add two differential forms of the same dimension as both were defined as sums to begin with.
We also do not define the multiplication of $\cdot$ two differential forms but we multiplying a form by a function is simply:
\begin{equation}
	(f \cdot \alpha) (x) = \sum_i f(x)\cdot a_i(x) \; dx_{i_1} \wedge \ldots \wedge dx_{i_p}
\end{equation}


Integrating over a $k$-form is quite simple.
First we shall consider integrating a $k$-form over a $k$-rectangle in $\mathbb{R}^k$.
Such a $k$-form is also known as a \emph{top-dimensional form}.
As we saw previously, any form of higher degree must be zero.
If $\omega$ is such a top form then we can always write
\begin{equation}
	\omega = f \; dx_1 \wedge \ldots \wedge dx_k
\end{equation}
for some function $f$.
Other presentations of $\omega$ exist, but we can always achieve such a presentation by commuting over $\wedge$ 
to the canonical ordering $x_1, \ldots, x_n$.
Once we have the $k$-form in this presentation, we just remove the wedges and evaluate the integral using the
integrand $f \; dx_1 \;dx_2 \ldots dx_k$.

\begin{definition}
Let $\alpha$ be a $k$-form on $\Omega \subset \mathbb{R}^n$ of the form $\alpha = A(x) \; \text{d}x_1 \wedge ... \wedge \text{d} x_n$.
If $A \in \mathcal{L}^1 (\Omega , \text{d}x)$ then we define:
\begin{equation}
\int_\Omega \alpha = \int_\Omega A(x) \; \text{d}x
\end{equation}
Where the left-hand side is the integral of a $k$-form and the right-hand side is a Lebesgue integral.
For any $\beta \in \Lambda^k (\Omega)$ we extend this definition linearly as the sum of integrals.
\end{definition}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% SINGULAR CUBES (or coordinate changes)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Singular Cubes}

Up until now we have been dealing with the very small set of axis aligned cubes.

\begin{definition}
	Manifold
\end{definition}

\begin{definition}
	Given a map $\varPhi : X \to Y$, $x \in X$ pushes forward to $\Phi(x) \in Y$
\end{definition}

Forms pull back from $Y$ to $X$

Benefit of differential forms is how cleanly they handle changes in coordinates.

This is generally done through the use of pull-backs.

A pullback $\varphi^* f$ can be thought of as \emph{functional precomposition}: $(\varphi^* f) (x) = f(\varphi(x))$


Gets its name from pulling $F$ back through $\omega$

\begin{definition}
$F: X \to \Omega$
Define the pullback $F^* \beta$
\begin{equation}
F^* \beta = \sum_j  b_j ( F(x)) (F^* \text{d}x_{j_1}) \wedge ... \wedge (F^* \text{d} x_{j_k})
\end{equation}
and
\begin{equation}
F^* \text{d}x_j = \sum_\ell \frac{\partial F^j}{\partial x_\ell} \; \text{d} x_\ell
\end{equation}
\end{definition}

Which can be reduced by:
\begin{align}
F^ * \beta & = \sum_j  b_j ( F(x)) (F^* \text{d}x_{j_1}) \wedge ... \wedge (F^* \text{d} x_{j_k}) \\
& = \sum_j  b_j ( F(x))  
\left( \sum_\ell \frac{\partial F^{j_1}}{\partial x_\ell} \; \text{d} x_\ell \right)
\wedge ... \wedge  
\left( \sum_\ell \frac{\partial F^{j_k}}{\partial x_\ell} \; \text{d} x_\ell \right) \\
& = ... \\
& = \sum_j b_j ( F(x)) \; \text{det}\left( J_F \right) \; \text{d}x_{j_1} \wedge ... \wedge \text{d} x_{j_k}
\end{align}

Which is significant given the change of variable formula for integration:

\begin{equation}
\int_{\phi(U)} \! f(v) \; dv = \int_U \! f(\phi(u)) \; |\text{det}\phi'(u)| \; du
\end{equation}

\begin{theorem}
Let $F : X  \to \Omega$ be an (orientation-preserving diffeomorphism) and $\alpha$ an integrable $n$-form on $\Omega$ then
\begin{equation}
\int_\Omega \alpha = \int_X F^* \alpha
\end{equation}
\end{theorem}

More algebra of differential forms

\begin{equation}
F^* (\alpha \wedge \beta ) = (F^* \alpha) \wedge (F^* \beta)
\end{equation}

\begin{definition}
Exterior derivative
\end{definition}

...

\begin{equation}
d(\alpha \wedge \beta) = (d \alpha) \wedge \beta + (-1)^j \alpha \wedge ( d \beta)
\end{equation}

...

\begin{equation}
F^* (d \beta ) = dF^* \beta
\end{equation}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% MANIFOLD INTEGRATION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integration on Singular Cubes}

\todo[inline]{Need introduction to manifolds somewhere.}

We have already seen standard $n$-cubes in the previous chapter.
Now that we have pull-backs we can define integration on the more general \emph{singular cube}
But first, what is a singular cube.


\begin{definition}
	Singular cube: differentiable map $c$ from standard $k$-cube to $k$-dimensional manifold.
\end{definition}

It is a common abuse of notation to use $c$ to also to refer to the image $c( [\![ 0,1]\!]^k ) \subseteq M$.
The choice of using specifically the standard $k$-cube is arbitrary.
A differentiable map $f$ from $[\![a,b]\!]$ can always be composed with $g:t \mapsto ta +(1-t)b$ 
to get singular cube $c=f \circ g$.
Gives us innumerably more shapes to work with.
Hemisphere for example is the singular 2-cube given by $(r, \varphi) \to r \cos(\pi \varphi) x+ r \sin(\pi \varphi) y$


\begin{definition}
	Let $c$ be a singular $k$-cube and $\omega$ a $k$-form on the image of $c$.
	Then we define the integral using $c^*(\omega)$ the pull-back of $\omega$ along $c$:
	\begin{equation}
		\int\displaylimits_c \omega 
		= \int\displaylimits_{c \left( [\![0,1]\!]^k \right)} \omega
		= \int\displaylimits_{[\![0,1]\!]^k} c^* \omega
	\end{equation}
\end{definition}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% MANIFOLD INTEGRATION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integration over Manifolds}

A manifold is nothing more than a collection of local charts diffeomorphic to $\mathbb{R}^n$

So we use pullbacks to turn a set of rectangles into a manifold while simultaneously applying the manifold's pullback.

Integration on oriented manifolds is just a careful application of Theorem 5.2.1

\begin{example}
Integrate an atlas with overlapping charts (using inclusion-exclusion)
\end{example}

\todo[inline]{partitions of unity}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% STOKE'S THEOREM
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stokes' Theorem}

\begin{equation}
	\int_{\partial M} \omega = \int_M d\omega
\end{equation}

Generalization of FTC, Greens, ...


Stokes' on $n$-cubes

Simplicial cubes.

Manifolds

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Contour Integral
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Example: \emph{Contour Integration}}
\todo[inline]{??????????}

Using Stokes' theorem and Inclusion/Exclusion to evaluate a tricky theorem like:

\begin{equation}
f(z) = \frac{z^2}{(z^2 + 2z + 2)}
\end{equation}

% http://en.wikipedia.org/wiki/Methods_of_contour_integration

 (2-3 pages)

\newpage
